---
title: "TidyTemplate"
date: 2021-04-13
output: html_output
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)

library(geojsonio)
#library(RColorBrewer)
library(rgdal)

library(broom)
library(rgeos)

library(viridis)
library(showtext)

font_add_google(name = "Oswald")

showtext_auto()
```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2021-04-13")

post_offices <- tt$post_offices

us_reps <- read_csv(file = "./data/us_reps_state.csv") %>% janitor::clean_names()
```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r}
skimr::skim(post_offices)
```


Just get the post offices that are still open
```{r Wrangle}
office_count <- post_offices %>%
  select(id, name, state, established, discontinued) %>%
  filter(is.na(discontinued)) %>%
  group_by(state) %>%
  summarize(offices = n(), .groups = "drop")

office_ratio <- us_reps %>%
  left_join(tibble(state = state.name, id = state.abb), by = "state") %>%
  left_join(office_count, by = c("id" =  "state")) %>%
  mutate(rep_ratio = offices / representatives_number,
         pop_ratio = pop / offices) %>%
  arrange(desc(pop_ratio))
  

```


# Visualize

Using your processed dataset, create your unique visualization.

```{r}
post_offices %>%
  filter(!is.na(discontinued)) %>%
  filter(discontinued < 2021) %>%
  ggplot(aes(x = discontinued)) +
  geom_histogram() +
  scale_x_continuous(limits = c(1800, 2021))
```


```{r Visualize}
# Download the Hexagones boundaries at geojson format here: https://team.carto.com/u/andrew/tables/andrew.us_states_hexgrid/public/map.

# Load this file. (Note: I stored in a folder called DATA)
spdf <- geojson_read("DATA/us_states_hexgrid.geojson",  what = "sp")

# Bit of reformating
spdf@data = spdf@data %>%
  mutate(google_name = gsub(" \\(United States\\)", "", google_name))

# Show it (requires rgdal library)
plot(spdf)
```

```{r}
# I need to 'fortify' the data to be able to show it with ggplot2 (we need a data frame format)
#library(broom)
spdf@data = spdf@data %>% mutate(google_name = gsub(" \\(United States\\)", "", google_name))
#spdf_fortified <- tidy(spdf, region = "google_name")

spdf_fortified <- tidy(spdf, region = "iso3166_2")

# Calculate the centroid of each hexagon to add the label:
library(rgeos)
centers <- cbind.data.frame(data.frame(gCentroid(spdf, byid=TRUE), id=spdf@data$iso3166_2))
 
# Now I can plot this shape easily as described before: (required package mapproj installed)
ggplot() +
  geom_polygon(data = spdf_fortified, aes( x = long, y = lat, group = group), fill="skyblue", color="white") +
  geom_text(data=centers, aes(x=x, y=y, label=id)) +
  theme_void() +
  coord_map()
```

```{r}
office_ratio %>%
  ggplot(aes(x = pop_ratio)) +
  geom_histogram(bins = 10)
```

```{r}
spdf_fortified <- spdf_fortified %>%
  left_join(select(office_ratio, id, pop_ratio), by = "id") %>%
  filter(!is.na(pop_ratio))

# Make a first chloropleth map
ggplot() +
  geom_polygon(data = spdf_fortified, aes(fill =  pop_ratio, x = long, y = lat, group = group)) +
  scale_fill_gradient() +
  theme_void() +
  coord_map()
```

```{r}
# Prepare binning
spdf_fortified$bin <- cut( spdf_fortified$pop_ratio , breaks=c(seq(0, 20000, 5000), Inf), 
                           labels=c("< 5K", "5-10K", "10-15K", "15-20K", "20K+") , include.lowest = TRUE )
```


```{r}
# Prepare a color scale coming from the viridis color palette

my_palette <- rev(magma(8))[c(-1,-8)]
 
# plot
p1 <- ggplot() +
  geom_polygon(data = spdf_fortified, aes(fill = bin, x = long, y = lat, group = group) , size=0, alpha=0.9) +
  geom_text(data=centers, aes(x=x, y=y, label=id), color="white", size=3, alpha=0.6) +
  theme_void() +
  scale_fill_manual( 
    values=my_palette, 
    name="Average population served per post office", 
    guide = guide_legend( keyheight = unit(3, units = "mm"), keywidth=unit(12, units = "mm"), label.position = "bottom", title.position = 'top', nrow=1) 
  ) +
  labs( title = "Population Served per Post Office ca. 2000",
        caption = "Graphic: @datadavidz | Source: Blevins and Helbock | #TidyTuesday") +
  theme(
    legend.position = c(0.5, 0.9),
    text = element_text(color = "#22211d"),
    plot.background = element_rect(fill = "#f5f5f2", color = NA), 
    panel.background = element_rect(fill = "#f5f5f2", color = NA), 
    legend.background = element_rect(fill = "#f5f5f2", color = NA),
    plot.title = element_text(family = "Oswald", size= 22, hjust=0.5, color = "#4e4d47", margin = margin(b = -0.1, t = 0.4, l = 2, unit = "cm")),
    plot.caption = element_text(hjust = 0.95, vjust = 1)
  )

p1
```


# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```
