---
title: "Break Free From Plastic"
date: 2021-01-27
output: html_output
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(ggthemes)

theme_set(theme_minimal())

```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2021-01-26")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```
Extract the only data table (plastics)
```{r}
plastics <- tt$plastics
```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

There are only two years of data: 2019 (9296 entries) and 2020 (4084 entries)
There are EMPTY country names (1346 entries).  Not sure what EMPTY means.
There is a parent company called "Grand Total" which doesn't seem to be a company name.

Does Grand Total equal the sum total for a country in 2019?
```{r Wrangle}
argentina_sum <- plastics %>% 
  filter(country == "Argentina", parent_company != "Grand Total") %>%
  group_by(country, year) %>% 
  summarize(across(empty:grand_total, sum)) %>%
  #summarize(hdpe = sum(hdpe)) %>%
  ungroup()

argentina_total <- plastics %>%
  filter(country == "Argentina", parent_company == "Grand Total") %>%
  select(country, year, empty:grand_total)

bind_rows(argentina_sum, argentina_total) %>% arrange(year)

```
Yes, parent_company as "Grand Total" was just the sum total for a country in that year.

Clean up the Country Name
```{r}
plastics <- plastics %>%
  mutate(country = str_to_title(country, locale = "en")) %>%
  mutate(country = ifelse(country == "Taiwan_ Republic Of China (Roc)", "Taiwan", country))
```


# Visualize

Using your processed dataset, create your unique visualization.

What are the top 10 countries participating in BFFP events?
```{r visualize}

plastics_subset <- plastics %>%
  select(country, year, volunteers) %>%
  distinct() %>%
  group_by(country) %>%
  summarize(total_vols = sum(volunteers), .groups = "drop") %>%
  arrange(desc(total_vols))
  
top_countries <- plastics_subset %>% 
  slice(1:10) %>%
  pull(country)

plastics %>%
  left_join(plastics_subset, by = "country") %>%
  filter(country %in% top_countries) %>%
  select(country, year, volunteers, total_vols) %>%
  distinct() %>%
  mutate(country = fct_reorder(country, total_vols)) %>%
  mutate(year = as_factor(year)) %>%
  mutate(year = fct_relevel(year, rev)) %>%
  ggplot(aes(x = volunteers, y = country, fill = year)) +
  geom_col() +
  labs(title = "Top 10 Countries Participating in BFFP Events",
       subtitle = "Volunteers at Plastic Clean-up Events (www.breakfreefromplastic.org)",
       caption = "Created by @datadavidz | Data Courtesy of Sarah Sauve | #TidyTuesday",
       x = "Number of Volunteers",
       y = NULL,
       fill = "Year") +
  theme_fivethirtyeight() +
  scale_fill_fivethirtyeight()

```


# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "top10countriesBFFP.png",
  device = "png")

```
