---
title: "TidyTemplate"
date: 2021-03-16
output: html_output
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)

library(lubridate)
library(ggridges)
library(ragg)
#library(systemfonts)
library(showtext)

library(ggfx)

font_add("Anton", "Anton-Regular.ttf")
showtext_auto()

theme_set(theme_light())
```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2021-03-16")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

games <- tt$games %>%
            mutate(gamename = str_to_title(gamename))
```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

overall conclusions
- 1258 different game names
- data from 2012-2021 but amount of data is increasing over time except 2021 is partial


```{r Wrangle}
tt$games %>%
  count(gamename, sort = TRUE)

tt$games %>% count(year, sort = TRUE)

tt$games %>% filter(str_detect(gamename, "^Tom Clancy's Rainbow Six Siege"))
```


Get the biggest increase Feb-Mar 2020
```{r}
top_surge_games <- games %>%
  filter(month == "March" & year == 2020) %>%
  arrange(desc(gain)) %>%
  slice(1:12) %>%
  pull(gamename)
```
 
```{r}
top_percent_increase <- games %>%
  filter(month == "March" & year == 2020) %>%
  filter(avg > 100000) %>%
  mutate(percent_increase = (avg / (avg - gain) - 1) * 100) %>%
  arrange(desc(percent_increase)) %>%
  slice(1:12) %>%
  pull(gamename)
```

 
```{r}
plot_data <- games %>%
  filter(gamename %in% top_percent_increase[1:5]) %>%
  mutate(gamename = factor(gamename, rev(top_percent_increase[1:5]))) %>%
  mutate(year_month = ymd(paste0(year,"/", month, "/", "1"))) %>%
  filter(year_month <= ymd("2020-9-01") & year_month >= ymd("2019-09-01")) %>%
  group_by(gamename) %>%
  arrange(gamename, year_month) %>%
  mutate(idx = row_number())
```

 
```{r}
plot_labels <- plot_data %>% 
  group_by(gamename) %>% 
  summarize(idx = 1,
            avg = 0,
            year_month = ymd("2019-06-01"),
            .groups = "drop")
```

```{r}
tt$games %>%
  filter(gamename %in% top_surge_games[1:3]) %>%

  mutate(year_month = ymd(paste0(year,"/", month, "/", "1"))) %>%
  # mutate(id = case_when(gamename == "Counter-Strike: Global Offensive" ~ 1,
  #                       gamename == "ARK: Survival Evolved" ~ 1,
  #                       gamename == "Dota 2" ~ 1,
  #                       TRUE ~ 0)) %>%
  ggplot(aes(x = year_month, y = 1)) +
  geom_ridgeline(aes(height = avg, group = factor(gamename), fill = factor(gamename)), alpha = 0.2)
  
```
Games with biggest pandemic surge Feb 2020 to March 2020
```{r}
tt$games %>%
  filter(month == "March" & year == 2020) %>%
  arrange(desc(gain))

tt$games %>%
  filter(month == "March" & year == 2020) %>%
  arrange(desc(avg))
```

Games with biggest pandemic surge Feb 2019 to March 2019
```{r}
tt$games %>%
  filter(month == "March" & year == 2019) %>%
  arrange(desc(gain))

tt$games %>%
  filter(month == "March" & year == 2019) %>%
  arrange(desc(avg))
```


Average six months before and after lockdown
```{r}
before_6mo <- tt$games %>%
  mutate(year_month = ymd(paste0(year,"/", month, "/", "1"))) %>%
  filter(year_month < ymd("2020-03-01") & year_month >= ymd("2019-09-01")) %>%
  group_by(gamename) %>%
  summarize(before = round(mean(avg), 0), .groups = "drop") %>%
  arrange(desc(before))
  
```
Average six months before and after lockdown
```{r}
after_6mo <- tt$games %>%
  mutate(year_month = ymd(paste0(year,"/", month, "/", "1"))) %>%
  filter(year_month < ymd("2020-9-01") & year_month >= ymd("2019-03-01")) %>%
  group_by(gamename) %>%
  summarize(after = round(mean(avg), 0), .groups = "drop") %>%
  arrange(desc(after))
  
```

```{r}
inner_join(before_6mo, after_6mo, by = "gamename") %>%
  filter(after > 10000) %>%
  mutate(increase = after - before) %>%
  mutate(percent_increase = (after/before - 1) * 100) %>%
  arrange(desc(percent_increase))
```

# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}
#gamestring <- "^Tom Clancy's Rainbow Six Siege"
#gamestring <- "^Brawlhalla"
#gamestring <- "^Rocket League"
#gamestring <- "^Lords Mobile"
#gamestring <- "^PLAYERUNKNOWN"
#gamestring <- "^Counter-Strike: Global"
#gamestring <- "^ARK: Survival"
#gamestring <- "Grand Theft Auto V"
#gamestring <- "^Football Manager 2020"
#gamestring <- "^Tomb Raider"
gamestring <- "Total War: THREE KINGDOMS"

tt$games %>% 
  filter(str_detect(gamename, gamestring)) %>%
  mutate(year_month = ymd(paste0(year,"/", month, "/", "1"))) %>%
  ggplot(aes(x = year_month, y = avg)) +
  geom_line()
  
```
How Jake Kaupp did the ridgelines
```{r}
# plot <- ggplot() +
#   as_reference(geom_text(data = labels, aes(x = idx, y = gamename, label = gamename), vjust = -0.1, hjust = 0, family = "Anton", size = 14, color = "#37323e"), 
#                id = "text") +
#   with_blend(geom_ridgeline(data =  plot_data, aes(y = gamename, x = idx, height = avg/1000000, group = gamename, color = gamename, fill = gamename), size = 0.1, alpha = 1, show.legend = FALSE, scale = 1.5),
#              bg_layer = "text", 
#              blend_type = 'xor')  + 
#   annotate("text", x = 1, y = 5, label = "A Three Player Battle Royale", family = "Anton", size = 16, hjust = 0, color = "#37323e") +
#   annotate("text", x = 1, y = 4.7, label = str_wrap("Taking the top spot in average players on Steam early in 2012, Dota 2 and CS:GO have been fighting for top draw in multiplayer online gaming. Then in 2017 a new contender, PUBG, entered the ring taking the crown for years until waning interest and a surge of more battle royale games entered the market.", 65), family = "Raleway", size = 6, hjust = 0, vjust = 1, color = "#37323e") +
#    labs(x = NULL, 
#        y = NULL,
#        caption = "**Data**: Steam | **Graphic**: @jakekaupp") +
#   scale_x_continuous(breaks = year_labels$idx, labels = year_labels$year, limits = c(0, 117)) +
#   scale_y_discrete(expand = c(0.01, 0)) +
#   scale_fill_manual(values = c("#bfbdc1","#6d6a75","#37323e")) +
#   scale_color_manual(values = darken(c("#bfbdc1","#6d6a75","#37323e"))) +
#   theme_jk(markdown = TRUE,
#            grid = FALSE,
#            base_family = "Bebas Neue",
#            ticks = TRUE,
#            base_size = 20) +
#   theme(axis.text.y = element_blank(),
#         axis.ticks.y = element_blank(),
#         plot.caption = element_markdown(hjust = 0.95))
```

```{r, fig.width = 7, fig.height = 7}
p <- ggplot() +
  as_reference(geom_text(data = plot_labels, aes(x = year_month, y = gamename, label = gamename),
                vjust = -0.1, hjust = 0, family = "Anton", size = 8, color = "#37323e"), id = "text") +
  with_blend(geom_ridgeline(data =  plot_data, aes(y = gamename, x = year_month, height = avg/1000000, group = gamename, 
                                        color = gamename, fill = gamename), size = 0.1, alpha = 1, show.legend = FALSE, scale = 1.5),
                                        bg_layer = "text", blend_type = "xor") +
  fishualize::scale_fill_fish_d(option = "Aulostomus_chinensis") +
  scale_y_discrete(expand = c(0.01, 0)) +
  scale_x_continuous(breaks = c(ymd("2020-03-01")), labels = "Lockdown") +
  theme(axis.text.x = element_text(family = "Anton", size = 12),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid.major.x = element_line(size = 3),
        panel.grid.major.y = element_blank(),
        panel.border = element_blank(),
        plot.title = element_text(family = "Anton", size = 28),
        plot.caption = element_text(hjust = 0.05)) +
  labs(title = "Pandemic Plays on Steam",
       subtitle = "Top Played Games 6 months before and after US Covid Lockdown",
       x = NULL,
       y = NULL,
       caption = "Graphic: @datadavidz | Source: Steam | #TidyTuesday")


p
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "TopSteamPlays.png",
  p,
  width = 7,
  height = 7,
  units = "in",
  device = ragg::agg_png())

```
