---
title: "TidyTemplate"
date: 2021-05-25
output: html_output
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE,
                      fig.showtext = TRUE)

library(tidyverse)
library(tidytuesdayR)

library(scales)
library(lubridate)

library(ggimage)
library(showtext)

theme_set(theme_light())

font_add_google(name =  "Press Start 2P", family = "nintendo")

showtext_opts(dpi = 320)
showtext_auto(enable = TRUE)

```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2021-05-25")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

records <- tt$records
drivers <- tt$drivers

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

65 players with records
16 tracks, most records at Wario Stadium (201), least records at Bowser's Castle (69)
There are three lap and single lap records

```{r Wrangle}
skimr::skim(drivers)
skimr::skim(records)

drivers %>% count(player, sort = TRUE)
records %>% count(player, sort = TRUE)

mario_kart <- records %>% 
  left_join(drivers %>% 
              select(position, player, total, nation) %>%
              distinct(), by = "player")

mario_kart %>% count(player, sort = TRUE)
mario_kart %>% count(track, sort = TRUE)
mario_kart %>% count(track, type, sort = TRUE)
```
Need to get top 5 drivers for each track
```{r}
#top driver time for each track
best_times <- mario_kart %>%
  filter(type == "Three Lap" & shortcut == "No") %>%
  group_by(track, player) %>%
  arrange(time) %>%
  slice_max(1) %>%
  ungroup()

#top drivers for complete race and no shortcut
top_drivers <- best_times %>%
  group_by(track) %>%
  arrange(time) %>%
  slice(1:2) %>%
  ungroup()

#calculate difference from top time
top_drivers <- top_drivers %>%
  group_by(track) %>%
  mutate(best_time = min(time)) %>%
  ungroup() %>%
  mutate(behind_leader = best_time - time)

```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}
mario_kart %>%
  mutate(penev = ifelse(player == "Penev", TRUE, FALSE)) %>%
  filter(shortcut == "No") %>%
  #filter(track == "Bowser's Castle") %>%
  ggplot(aes(x = date, y = time, color = penev)) +
  geom_point() +
  facet_wrap(~type)

  
```


```{r, fig.width = 7, fig.height = 5}
p1 <- top_drivers %>%
  filter(track %in% c("Wario Stadium", "Rainbow Road", "D.K.'s Jungle Parkway", "Yoshi Valley")) %>%
  mutate(track = str_wrap(track, 10)) %>%
  ggplot(aes(x = behind_leader, y = track)) +
  geom_text(aes(label = player), vjust = -1.75, family = "nintendo", size = 3, color = "gray90") +
  geom_image(image = "./img/mario_kart2.png", size = 0.15) +
  scale_x_continuous(limits = c(-0.125, 0.025))  +
  geom_vline(xintercept = 0.0125, color = "gray50", size = 1, linetype = "dashed") +
  annotate("text", x = 0.0225, y = 2.5, label = "FINISH", color = "gray80", family = "nintendo", angle = 270) +
  labs(title = "Mario Kart 64 World Records",
       subtitle = "Complete Race Record Holder and Runner-Up",
       caption = "Graphic: @datadavidz | Source: Mario Kart World Records | #TidyTuesday",
       x = "sec behind leader",
       y = NULL) +
  theme(plot.background = element_rect(fill = "gray20"),
        panel.background = element_rect(fill = "gray20"),
        
        axis.text = element_text(family = "nintendo", color = "gray90"),
        #axis.title.x = element_text(margin = margin(t = 0, r = 0, b = 10, l = 0)), 
        axis.title.x = element_text(family = "nintendo", size = 10, color = "gray90", margin = margin(t = 5, r = 0, b = 10, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 5, b = 0, l = 10)),
        axis.ticks = element_line(size = 1),
        plot.title = element_text(family = "nintendo", color = "gray90"),
        plot.subtitle = element_text(family = "nintendo", size = 10, color = "gray90"),
        plot.caption = element_text(family = "nintendo", size = 6, color = "gray85"),
        panel.border = element_rect(size = 3),
        panel.grid = element_blank(),
        plot.margin = unit(c(t = .1, r = .1, b = .1, l = .1), units = "in")
        
        )

p1
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}
ragg::agg_png(filename = "Mario_Kart_WR.png", width = 7, height = 5, units = "in", res = 320)
p1
dev.off()
```
